Meta-analysis

### 2019-11-01 04_Prep_data.Rmd
column names and variable formating updated. Output data file changed to `data/1902 PM_MB_means&Ygains.csv`

```{r}
library(dplyr)
library(readr)
```

```{r Calculate_yield-gains}
source("R/import_data.R")
PM_MB_means <- import_data()

PM_MB_means$grain_yield.t.ha. <-
   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data

for (i in levels(as.factor(PM_MB_means$Trial_ref))) {
   dat1 <- PM_MB_means[PM_MB_means$Trial_ref == i, ]

   if (any(is.na(unique(dat1$row_spacing)))) {
      warning(
         paste(
            unique(dat1$Trial_ref),
            "at",
            unique(dat1$Location),
            "in year",
            unique(dat1$Year),
            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
         )
      )
      next()
   }

   for (j in unique(dat1$row_spacing)) {
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$Fungicide == "control", "grain_yield.t.ha."])

@@

      dat2[dat2$Fungicide == "control", c("yield_gain", "prop_YG")] <-
         NA

      dat1[dat1$row_spacing == j, ] <- dat2
   }
   PM_MB_means[PM_MB_means$Trial_ref == i, ] <- dat1
}

# caluculate yield gain and prop_yield gain for experiments with no row spacing data
dat1 <- PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ]
controlY <-
   mean(dat1[dat1$Fungicide == "control", "grain_yield.t.ha."])
dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
dat1$prop_YG <- dat1$yield_gain / controlY
dat1[dat1$Fungicide == "control", c("yield_gain", "prop_YG")] <- NA
PM_MB_means[PM_MB_means$Trial_ref == "AM1303", ] <- dat1

write.csv(PM_MB_means,
          "data/1902 powdery mildew-Mungbean - Collated means.csv")
```

>>>>

```{r load_libraries}
library(dplyr)
library(readr)
```

```{r import_data}
source("R/import_data.R")
PM_MB_means <- import_data()
```

Data from `r length(PM_MB_means$trial_ref)` trials were collected and the means of each treatment calculated (`R/Cleaning historical data.R`). These data were combined into one file `1902 powdery mildew-Mungbean - Collated means.csv`.

```{r Calculate_yield-gains}
PM_MB_means$grain_yield.t.ha. <-
   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data

for (i in unique(PM_MB_means$trial_ref)) {
   dat1 <- PM_MB_means[PM_MB_means$trial_ref == i, ]

   if (any(is.na(unique(dat1$row_spacing)))) {
      warning(
         paste(
            unique(dat1$trial_ref),
            "at",
            unique(dat1$location),
            "in year",
            unique(dat1$year),
            "has unknown row.spacing (NA)\n 'yield_gain' and 'proportional yield gain' not calculated\n"
         )
      )
      next()
   }

   for (j in unique(dat1$row_spacing)) {
      dat2 <- dat1[dat1$row_spacing == j, ]
      controlY <-
         mean(dat2[dat2$fungicide == "control", "grain_yield.t.ha."])

@@

      dat2[dat2$fungicide == "control", c("yield_gain", "prop_YG")] <-
         NA

      dat1[dat1$row_spacing == j, ] <- dat2
   }
   PM_MB_means[PM_MB_means$trial_ref == i, ] <- dat1
}

# ____________________________________________
# calculate yield gain and prop_yield gain for experiments with no row spacing data

# dat1 <- PM_MB_means[PM_MB_means$trial_ref == "AM1303", ]
# 
# controlY <-
#    mean(dat1[dat1$fungicide == "control", "grain_yield.t.ha."])
# 
# dat1$yield_gain <- dat1$grain_yield.t.ha. - controlY
# dat1$prop_YG <- dat1$yield_gain / controlY
# dat1[dat1$fungicide == "control", c("yield_gain", "prop_YG")] <- NA
# PM_MB_means[PM_MB_means$trial_ref == "AM1303", ] <- dat1

write.csv(PM_MB_means,
          "data/1902 PM_MB_means&Ygains.csv")
```
